WDIAS : A Microservices-Based Weather Data Integration and Assimilation System\\

### 2020-05-07 ThePaper.tex

\begin{IEEEkeywords}
\db{Cloud computing, data assimilation, data integration, }microservice, weather
\end{IEEEkeywords}
\dbc{Update keyword list based on thesis. 4-5 keywords max}
\gkc{Thesis keywords are Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather. Do we need different set of keywords?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{pse:Introduction}
Weather prediction is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources. To enhance the accuracy of weather predictions, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s. Before feeding such diverse data collected from different sources, we need to convert data into NWMs compatible data format. Further we need to process data with lesser time to increase the lead time of forecasting, and need to handle bulk stream weather data.
Many third-party applications and researcher need to accessed processed weather data to make use of them. As few examples, logistics companies could use those data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
Even though there are many data integration systems, most systems are proprietary or closed source. For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated countries, those systems need to be highly customized. Thus, it required to get support from the vendor to integrate and configure the system.
Most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, and not using modern architecture pattern like microservice architecture that can use to build highly scalable and available systems, and use containerized applications to run systems independ of software platforms.

>>>>

\begin{IEEEkeywords}
\db{Cloud computing, data assimilation, data integration, }microservice, weather
\end{IEEEkeywords}
\dbc{Update keyword list based on thesis. 4-5 keywords max}
\gkc{Thesis keywords are Cloud computing, data assimilation, data integration, hierarchical databases, microservice, weather. Do we need different set of keywords?}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{pse:Introduction}
Weather forecast is essential to reduce the impacts caused by natural disasters and to effectively manage natural water resources. To enhance the accuracy of weather forecast, it requires to provide reliable and detailed weather data as inputs to \acrfull{nwm}s. Before feeding such diverse data collected from different sources, we need to convert data into NWMs compatible data format. Further we need to process data with lesser time to increase the lead time of forecasting, and need to handle bulk stream weather data.
Many third-party applications and researcher need to accessed processed weather data to make use of them. As few examples, logistics companies could use those data with their models to plan and schedule their deliveries. Agricultural insurance companies can warn the farmers, as well as calculate premiums based on anticipated weather patterns.
Even though there are many data integration systems, most systems are proprietary or closed source. For an island like Sri Lanka that having different kinds of weather seasons over the year than that software originated countries, those systems need to be highly customized. Thus, it required to get support from the vendor to integrate and configure the system.
Most of the software existing out there are not up to date with the latest technology concepts such as Cloud Computing, and not using modern architecture pattern like microservice architecture that can use to build highly scalable and available systems, and use containerized applications to run systems independ of software platforms.

### 2020-05-07 introduction/sec_1-motivation.tex
Updates from Overleaf

Weather prediction is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water. 
%It will give more understanding of weather prediction if we look into a weather prediction workflow that can use to predict the surface water level. 
The weather predictions/forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the most fitting model is selected. After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators. For example, FLO2D, a hydrologic model that predicts surface water level, could use precipitation estimates from \acrshort{wrf} to forecast flood levels.

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems. \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.
\dbc{Tru to use ``weather forecast'' than ``weather prediction''}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert them to a data format that can be ingest by the models. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

>>>>

Weather forecast is essential to reduce the impact caused by natural disasters and to effectively manage natural resources like water.
The weather forecasts are performed using \acrfull{nwm} that use a set of configuration parameters and the current status of the environment such as temperature, rainfall, and wind direction as the inputs. For example, the \acrfull{wrf} \cite{MesoscaleMicroscaleMeteorologyLaboratoryWeatherModel} model is used to predict the rainfall, temperature, and wind direction. Typically multiple \acrshort{nwm} are executed on the same data with different configuration parameters. Then using the real-time observations, the most fitting model is selected. After removing the bias, the data extracted from a \acrshort{nwm} are then fed into another set of models/simulators. For example, FLO2D, a hydrologic model that predicts surface water level, could use precipitation estimates from \acrshort{wrf} to forecast flood levels.

\acrfull{curw} \cite{CUrWSL2017SL} is tasked with the mission to reduce water-related natural disasters in Sri Lanka. \acrshort{curw} \cite{CUrWSLObservedSL} is implementing own system with the idea of long-term maintainability rather than depending on existing weather data integration systems. \acrshort{curw} collects real-time data from weather stations and other relevant entities and generates daily forecasts. Then the generated results are shared with relevant public departments responsible for disaster planning, risks mitigation, and disaster management. One of the future goals of \acrshort{curw} is to open up data to the public enabling both societal and commercial use cases.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Motivation}
To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to \acrshort{nwm}. These NWMs utilize multi-modal weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Before feeding such diverse data (collected from different sources that belong to different stakeholders) into respective NWMs, it is necessary to convert them to a data format that can be ingest by the models. Moreover, the data integration system's response time needs to be relatively low to forecast and monitor time-sensitive weather events like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

### 2020-05-07 method/sec_0_introduction.tex
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should be capital if used li

To get an overall idea of the flow of weather prediction, let us look into one of the weather forecastings flows using the \acrshort{curw} \cite{CUrWSL2017SL}.

@@

\subsubsection{Integration }
The system should be capable of integrating data from different sources such as satellite data, high end, and low-end weather station. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data. Thus the system should store the bulk data while optimizing the disk space.
\subsubsection{Dissemination}
Then different users should be able to retrieve data as they require. Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on Geo queries.

>>>>

To get an overall idea of the flow of weather forecast, let us look into one of the weather forecastings flows using the \acrshort{curw} \cite{CUrWSL2017SL}.

@@

\subsubsection{Integration }
The system should be capable of integrating data from different sources such as satellite data, high end, and low-end weather station. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally.
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data. Thus, the system should store the bulk data while optimizing the disk space.
\subsubsection{Dissemination}
Then different users should be able to retrieve data as they require. Also, the users should be able to easily search into the available information in the system based on timeseries metadata or based on Geo queries.

### 2020-05-07 structure.tex
Plagiarism: Ack fix
Added fixes
Error Term,Correct Term,Description,No of Occurrences,Pages (absolute)
a.k.a.,aka.,,Shoudl be aka and need a comma,1,-1
[a-z] as well as,, as well as,Needs a comma before,3,-1
Also,Also,,Comma should be used at beginning of a sentence,1,-1
can not,cannot,Is a single word,4,-1
[fF]igure.\d,Figure n,There has to be a space like Figure 2.7,82,-1
Hence,Hence,,Comma should be used at beginning of a sentence,1,-1
in order to,to,Can be replaced with just to in many cases,4,-1
in to,into,Is a single word,1,-1
may be,maybe,Is a single word,2,-1
section,Section,S should b

To enhance the accuracy of weather predictions, it is necessary to provide reliable and detailed weather data as inputs to Numerical Weather Models (NWM). These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

@@

I also dedicate this thesis to my many friends at CUrW SL who have supported and be with me during this period of time. Also special thanks to Dr. Dilum Bandara and Dr. Srikantha Herath for giving me this wonderful oppotunity to expore this new domain.

@@

Introduce your thesis here.
\begin{figure}
\begin{center}
  \includegraphics[width=1in]{orchids.jpg}\\
  \caption{A picture of an orchid.}\label{fi:orchid}
\end{center}
\end{figure}
Figure \ref{fi:orchid} shows an orchid.

>>>>

To enhance the accuracy of weather forecast, it is necessary to provide reliable and detailed weather data as inputs to Numerical Weather Models (NWM). These NWMs utilize weather data collected via diverse sources such as automated weather stations, radars, air balloons, and satellite images. Prior to feeding such diverse data (collected from different sources that belongs to different stakeholders) into respective NWMs, it is necessary to integrate data into a common format. Moreover, the data integration system’s response time need to be relatively low to accommodate critical situations like hurricanes, storms, and floods which require rapid and frequent execution of NWMs.

@@

I also dedicate this thesis to my many friends at CUrW SL who have supported and be with me during this period of time. Also, special thanks to Dr. Dilum Bandara and Dr. Srikantha Herath for giving me this wonderful oppotunity to expore this new domain.

@@

Introduce your thesis here.
\begin{figure}
\begin{center}
  \includegraphics[width=1in]{orchids.jpg}\\
  \caption{A picture of an orchid.}\label{fi:orchid}
\end{center}
\end{figure}
\cref{fi:orchid} shows an orchid.
